Code Publishing Tutorial

### 2024-11-27 index.qmd
Mention Org Mode and StatTag

Quarto is a tool to create reproducible documents, but not the only one. You may also use [RMarkdown](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), or one of the countless others.
:::

>>>>

Quarto is a tool to create reproducible documents, but not the only one. You may also use [RMarkdown](https://rmarkdown.rstudio.com/), [Jupyter Book](https://jupyterbook.org/), [Stencila](https://stencila.io/), [Curvenote](https://curvenote.dev/), [showyourwork!](https://show-your.work/), [Org Mode](https://orgmode.org/), [StatTag](https://sites.northwestern.edu/stattag/), or one of the countless others.
:::
